    %-------------------------------------------------------------Experience
    \begin{tcolorbox}[title=Experience \faBriefcase, colframe=blue!25!black]

        \textbf{Test Engineering Group Lead}\\
        \faMapMarker \hspace{0mm} \href{https://www.intel.com/content/www/us/en/corporate-responsibility/intel-in-costa-rica.html}{Intel, Costa Rica}  \hspace{11.5cm} \faCalendar \hspace{0mm} 2024-Present \\
        \textit{I am responsible for coordinating key activities at Intel Foundry Costa Rica, specifically in the Testing department. In this role, I oversee activities such as Test Program deployments, Reject Validation, Enabling Routes, and similar processes for both New Product Introduction and High Volume Manufacturing. I frequently review KPIs with my team, and together we continuously seek ways to improve. Additionally, it is my responsibility to support my team’s career growth, whether on the managerial or technical path.}
        
        \tcbline

        \textbf{Technical Support Engineer}\\
        \faMapMarker \hspace{0mm} \href{https://www.ibm.com/mx-es}{IBM, Costa Rica}  \hspace{11.5cm} \faCalendar \hspace{0mm} 2024 (Jan-Mar) \\
        \textit{In this role, I provide technical support for IBM’s \href{https://www.ibm.com/products/safer-payments}{Safer Payments} application. This application runs on Red Hat Enterprise Linux (RHEL). I resolve tickets for customers around the world (Americas, Asia, Europe, etc.). I coordinate meetings and troubleshoot issues with both the customer and the DevOps team. Customer service and problem-solving skills are essential in this role.}
        
        \tcbline
        
        \textbf{High Volume Engineer}\\
        \faMapMarker \hspace{0mm} \href{https://www.intel.com/content/www/us/en/corporate-responsibility/intel-in-costa-rica.html}{Intel, Costa Rica}  \hspace{11.6cm} \faCalendar \hspace{0mm} 2021-2024 \\
        \textit{I was responsible for the deployment of new test programs in the fabric's tools. This helps ensure a high quality standard for the microprocessors provided to customers worldwide. Several activities are involved in these test program deployments, including coordinating with different departments within the company, ensuring hardware and software requirements are met, debugging logs, problem-solving, big data analysis, and more. My technical and interpersonal skills have improved both as an engineer and as a leader.}
        
        \tcbline
        
        \textbf{Sales \& Service Engineer} \\
        \faMapMarker \hspace{0mm} \href{https://electromotores.com/}{Electromotores de Costa Rica}  \hspace{9.8cm} \faCalendar \hspace{0mm} 2021 (Apr-Sep)\\
        \textit{This role includes travel both inside and outside the country, with the goal of performing tests (ground insulation, ohmic resistance, surge, partial discharges) on electrical machines. It also involves preparing reports based on the collected data and verifying whether the results meet international standards (IEEE). Clear and effective communication with the client is fundamental.}%Recently we went to Guatemala for a whole month, to a hydroelectric power plant.

        \tcbline

        \textbf{Python Developer}: Photovoltaic Energy Course Assistant\\
            \faMapMarker \hspace{0mm} \href{https://eie.ucr.ac.cr/}{Escuela de Ingeniería Eléctrica, UCR}  \hspace{8.8cm} \faCalendar \hspace{0mm} 2020\\ \textit{In this role, I migrated a MATLAB code to \href{https://github.com/Jimenez96Vega/Photovoltaic_System.git}{Python}. Using mathematical models and Python libraries (NumPy, Astropy, Matplotlib), the program was able to calculate the optimal rotation and inclination angles for a solar panel based on a given position on the planet. As an assistant, I also created video tutorials for the students, explaining the physics of the problem and a possible solution in code.}   

    \end{tcolorbox}
    
        %-------------------------------------------------------------Experience
    \begin{tcolorbox}[title=Experience \faBriefcase, colframe=blue!25!black]
        
        \textbf{Manufacturing Engineer Intern}\\
        \faMapMarker \hspace{0mm} \href{https://www.bostonscientific.com/en-US/Home.html}{Boston Scientific, Costa Rica}  \hspace{10.3cm} \faCalendar \hspace{0mm} 2020 - 2021\\
        \textit{This internship has further strengthened my soft skills, as manufacturing roles require precise and frequent communication between product builders, the core team, managers, and other departments such as equipment, calibration, and shipping. My activities focused on improving line production (high volume) while maintaining the high quality standards required for the medical industry (heart devices). Recognizing the importance of effective time management, I implemented a Python script that automates yield calculation (good units per total units) and the construction of a Pareto graph, which saved both time and effort each day.}
        
        \tcbline
        
        \textbf{Cashier}\\
        \faMapMarker \hspace{0mm} \href{https://maxipali.co.cr/}{Maxi Palí, Grecia} \hspace{12cm} \faCalendar \hspace{0mm} 2014-2015 \\
        \textit{In this job, I made sure that all customers found what they wanted from the store (clothes, fruits, beverages, etc.) and handled their payments. Every interaction with customers was a great opportunity to improve my soft skills.}
       
        
    \end{tcolorbox}